An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-03-14 EconGrowth-R-Functions.Rnw
Now doing a double-y graph for the gamma plots.

#############################
# This function creates a series of graphs for Cobb-Douglas with energy functions
# showing various parameters as a function of gamma.
# countryAbbrev tells which country you want to view
# energyType tells which type of energy you want
# textScaling tells how you want to scale the text on the axes and other places.
##
cdeGridGraphs <- function(countryAbbrev, energyType, textScaling=1.0){
  gammaGrid <- seq(0.0, 0.95, by=0.05)
  data <- cdeGridData(countryAbbrev, energyType, gammaGrid)
  # Now melt the data so that it is in the correct form.
  data_molten <- melt(data, id="gamma")
  alphaBetaGammaRange <- c(0.0, 1.0)
  alphaBetaGammaTics <- c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)
  lambdaRange <- c(0.0, 0.004)
  lambdaTics <- c(0.0, 0.001, 0.002, 0.003, 0.004)
  sseRange <- c(0.0, 0.08)
  sseTics <- c(0.0, 0.02, 0.04, 0.06, 0.08)
  # Create a lattice graph that shows the four variables (lambda, alpha, beta, and SSE) vs. gamma.
  graph <- xyplot(value ~ gamma | variable, data=data_molten,
                  # 1=lambda, 2=alpha, 3=SSE, 4=beta
                  index.cond=list(c(3,1,2,4)), #orders the panels as SSE, lambda, alpha, beta.
                  strip = strip.custom(factor.levels=c("$\\lambda$", "$\\alpha$", "$SSE$", "$\\beta$"), 
                                       bg="transparent", # Sets background transparent to match the graph itself.
                                       par.strip.text=list(cex=textScaling) # Scales text in the strip.
                                       ),
                  as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
                  pch = c(1), col.symbol = c("black"), #Controls symbol parameters
                  scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
                              tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
                              x=list(relation="free",
                                     at=alphaBetaGammaTics),
                              y=list(relation="free",  #allows each axis to be different
                                     #specifies location for tics
                                     at=list(lambdaTics, alphaBetaGammaTics, sseTics, alphaBetaGammaTics))
                              ), 
                  ylim=list(lambdaRange, alphaBetaGammaRange, sseRange, alphaBetaGammaRange), #y axis limits
                  #axis labels and scaling
                  xlab=list(label="$\\gamma$", cex=textScaling), 
                  ylab=list(label="")
                  )
  return(graph)
}

>>>>

# This function creates a graph for Cobb-Douglas with energy functions. The graph has 
# a double Y axis. The first Y axis has alpha, beta, and gamma vs. gamma. The second Y axis
# has SSE vs. gamma.
# countryAbbrev tells which country you want to view
# energyType tells which type of energy you want
# textScaling tells how you want to scale the text on the axes and other places.
# This 
cdeGridGraphs <- function(countryAbbrev, energyType, textScaling=1.0){
  gammaGrid <- seq(0.0, 0.95, by=0.05)
  data <- cdeGridData(countryAbbrev, energyType, gammaGrid)
  # Now melt the data so that it is in the correct form.
  data_molten <- melt(data, id="gamma")
  alphaBetaGammaRange <- c(0.0, 1.0)
  alphaBetaGammaTics <- c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)
  lambdaRange <- c(0.0, 0.004)
  lambdaTics <- c(0.0, 0.001, 0.002, 0.003, 0.004)
  sseRange <- c(0.0, 0.08)
  sseTics <- c(0.0, 0.02, 0.04, 0.06, 0.08)
  # Create a lattice graph that shows the four variables (lambda, alpha, beta, and SSE) vs. gamma.
#   graph <- xyplot(value ~ gamma | variable, data=data_molten,
#                   # 1=lambda, 2=alpha, 3=SSE, 4=beta
#                   index.cond=list(c(3,1,2,4)), #orders the panels as SSE, lambda, alpha, beta.
#                   strip = strip.custom(factor.levels=c("$\\lambda$", "$\\alpha$", "$SSE$", "$\\beta$"), 
#                                        bg="transparent", # Sets background transparent to match the graph itself.
#                                        par.strip.text=list(cex=textScaling) # Scales text in the strip.
#                                        ),
#                   as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
#                   pch = c(1), col.symbol = c("black"), #Controls symbol parameters
#                   scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
#                               tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
#                               x=list(relation="free",
#                                      at=alphaBetaGammaTics),
#                               y=list(relation="free",  #allows each axis to be different
#                                      #specifies location for tics
#                                      at=list(lambdaTics, alphaBetaGammaTics, sseTics, alphaBetaGammaTics))
#                               ), 
#                   ylim=list(lambdaRange, alphaBetaGammaRange, sseRange, alphaBetaGammaRange), #y axis limits
#                   #axis labels and scaling
#                   xlab=list(label="$\\gamma$", cex=textScaling), 
#                   ylab=list(label="")
#                   )
#   return(graph)
  abgGraph <- xyplot(alpha+beta+gamma ~ gamma, data=data,
#                    pch = c(1), col.symbol = c("black"), #Controls symbol parameters
                                 x=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)), #location for x tics
                                 y=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0))  #location for y tics
                     ylim=c(0.0, 1.5), #y axis limits
                     xlab=list(label="$\\gamma$", cex=textScaling), 
                     ylab=list(label="$\\lambda$, $\\alpha$, $\\beta$")
  sseGraph <- xyplot(SSE ~ gamma, data=data,
                     pch = c(1), col.symbol = c("black"), #Controls symbol parameters
                                 y=list(at=c(0.0, 0.02, 0.04, 0.06, 0.08))  #location for y tics
                     ylim=c(0.0, 0.08),
                     ylab=list(label="$SSE$")
  doubleYGraph <- doubleYScale(abgGraph, sseGraph, add.ylab2=TRUE)
  return(doubleYGraph)
